---
title: Data Visualization--Lineplot & Violinplot
author: ''
date: '2020-03-10'
slug: lineplot
categories:
  - R
tags:
  - Data Visualization
---
Examples : **The weight of chicks from different months and feed diet**.
   
Firstly, have a look at dataset. The **structure of dataset** is following:

```{r code1, echo=TRUE, message=FALSE, warning=FALSE}
setwd("C:/blog/Dataset")
# library
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
Chick_data <- ChickWeight

str(Chick_data)
```

Then, have a look at the first 5 lines in datasets, we could find the dataset includes **weight**, **chick numbers**, **diet** and **times** variables.

```{r code2}
head(Chick_data, n =5)
```

## Line plot

**To explore the relationship between weight and time using package ggplot2**

```{r code3, echo=TRUE, message=FALSE, warning=FALSE}
g1 <- ggplot(data = Chick_data,aes(x = Time, y = weight, color = Chick)) +
  geom_point(size = 3L)+
  geom_line()+
  labs(title="Plot of Chick weight and Time",
       x = "Time", y = "Weight",color = "Chick code") +
  theme_bw()+
  theme(
    plot.title = element_text(color="black", size=14, face="bold.italic"),
    axis.title.x = element_text(color="black", size=14, face="bold"),
    axis.title.y = element_text(color="black", size=14, face="bold")
  )
g1
```

The results from plot indicated that the weight incresed with the increasing times.

## Violin plot

**To explore the relationship between weight and time using violin plot**


```{r code4, echo=TRUE, message=FALSE, warning=FALSE}
g2 <- ggplot(data = Chick_data,aes(x = Diet, y = weight, fill = Diet)) +
  geom_violin(aes(fill = factor(Diet)))+
  geom_boxplot(width=0.1)+
  labs(title="Plot of Chick weight and Feed diet",
       x = "Diet", y = "Weight",color = "Feed Diet") +
  theme_bw()+
  theme(
    plot.title = element_text(color="black", size=14, face="bold.italic"),
    axis.title.x = element_text(color="black", size=14, face="bold"),
    axis.title.y = element_text(color="black", size=14, face="bold")
  )
g2

```