---
title: Principal component analysis
author: ''
date: '2021-01-09'
slug: pca
categories:
  - R
tags:
  - Data analysis
---
## Principal component analysis(PCA)
From this section, the machine learning will be discussed by foods data, the data from Mid-infrared spectroscopy will be used for Geographical origin of Extra Virgin Olive Oils (Quadram open dataset,2003).

## Load dataset

```{r workspace}
## Load date
setwd("C:/blog/Dataset")

oil <- read.csv('FTIR_Spectra_olive_oils.csv',header = F, 
                stringsAsFactors = T)

print(oil[1:10,1:5])
```

## Data wrangling

The raw data form are not suitable for R programming, therefore we need to transpose it to suitable form.

```{r data wrangling, echo=TRUE, message=FALSE, warning=FALSE}
## data transpose
oil_transpose <- as.data.frame(t(oil))

print(oil_transpose[1:10,1:5])
## rename some col names to make data analysis easier

colnames(oil_transpose)=oil_transpose[1,]
oil_transpose <- oil_transpose[-1,]
library(dplyr)
oil_transpose <- rename(oil_transpose,c("Group" ="Group Code:",
                                        "Number" ="Sample Number:",
                                        "Countries" ="Wavenumbers"))
## Get transposed dataset

oil.data <- oil_transpose

print(oil.data[1:10,1:5])

```

## Principal Component Analysis

The PCA is used to reduce the dimensionality of the spectral value, and initially explore the distribution of the sample.

The original data and related transformated data (MSC, SNV and Savitzky-Golay filtering) are used to obtain the PCA plots.

```{r code9, echo=TRUE, message=FALSE, warning=FALSE}
library(factoextra)
library(FactoMineR)
library(ggrepel)
library(ggplot2)
library(prospectr)
```

## Raw data PCA

Have a look at spectral of different pre-processing for MIR.

```{r pca col, echo=TRUE}
colors = c("#CD0000", "#EE7600", "#FFFF00", "#008B45")
col <- as.factor(oil.data$Countries)
group <- c("Greece","Italy","Portuga", "Spain")

```

**RAW spectral**

```{r code10, message=FALSE, warning=FALSE}
raw_spc <- oil.data[,4:573]

x <- as.numeric(colnames(raw_spc))
y <- t(raw_spc[ , ])

par(mar=(c(5,7,4,2)))

matplot(x, y,col = colors,
        type = 'l', lty = 1,
        xlab = 'Wavelength (nm)', ylab = 'Absorbance',main = "Raw",
        font.lab = 1,
        cex.main = 1, cex.axis = 1, cex.lab=2)
legend("topleft",
       title = "Country",
       xpd = F,ncol = 1,
       legend = group,
       col = col,
       fill = colors,
       bty = "n",
       cex = 1.5,
       text.col = "black", text.font = 1,
       horiz = F)

p1 <- recordPlot()
```


```{r code11,echo=TRUE}
df_raw <- oil.data[,4:573]

df <- as.data.frame(apply(df_raw, 2, as.numeric))
print(df[1:10,1:5])
```

## Standard Normal Variate

```{r pca snv}
df_snv <- standardNormalVariate(df)

oil.snv <- cbind(oil.data[,1:3], df)
```
**SNV spectral**

```{r code14, message=FALSE, warning=FALSE}
x <- as.numeric(colnames(oil.snv))
y <- t(oil.snv[ , ])

par(mar=(c(5,7,4,2)))

matplot(x, y,col = colors, ylim = c(0,2),
        type = 'l', lty = 1,
        xlab = 'Wavelength (nm)', ylab = 'Absorbance',main = "SNV",
        font.lab = 1,
        cex.main = 1, cex.axis = 1, cex.lab=2)
legend("topleft",
       title = "Country",
       xpd = F,ncol = 1,
       legend = group,
       col = col,
       fill = colors,
       bty = "n",
       cex = 1.5,
       text.col = "black", text.font = 1,
       horiz = F)

p3 <- recordPlot()
```
p3

## The PCA plot of SNV Spectral

```{r code 15, fig.show='hide'}
oil.snv.pca <- PCA(oil.snv[,4:563],scale.unit = TRUE,ncp = 5,graph = TRUE)
```


```{r code16}
g3 <- fviz_pca_ind(oil.snv.pca, geom.ind = "point",
                   col.ind = oil.snv$Countries, # color by groups
                   palette = 'jco',
                   addEllipses = TRUE, ellipse.type = "convex",
                   legend.title = "Groups")+
  ggtitle("Oil - geographical-SNV")

g3
```

