---
title: Discrimination model (PLS-DA)
author: ''
date: '2021-04-08'
slug: PLSDA
categories:
  - R
tags:
  - Data analysis
  - data science
---
## Discrimination analysis

 Examples: **Using PLS-DA for geographical origin of oils**
 
 Dataset: Mid-infrared spectroscopy of Extra Virgin Olive Oils for Geographical origin discrimination analysis (Quadram open dataset,2003).

## Data preprocess

```{r workspace, message=FALSE, warning=FALSE}
## Load date
setwd("C:/blog/Dataset")

oil <- read.csv('FTIR_Spectra_olive_oils.csv',header = F, 
                stringsAsFactors = T)

print(oil[1:10,1:5])

## data transpose
oil_transpose <- as.data.frame(t(oil))

print(oil_transpose[1:10,1:5])
## rename some col names to make data analysis easier

colnames(oil_transpose)=oil_transpose[1,]
oil_transpose <- oil_transpose[-1,]

library(dplyr)

oil_transpose <- rename(oil_transpose,c("Group" ="Group Code:",
                                        "Number" ="Sample Number:",
                                        "Countries" ="Wavenumbers"))
## Get transposed dataset

oil.data <- oil_transpose

print(oil.data[1:10,1:5])

df_raw <- oil.data[,4:573]

df <- as.data.frame(apply(df_raw, 2, as.numeric))
str(df)
print(df[1:10,1:5])

## SNV transformation
library(prospectr)
df_snv <- standardNormalVariate(df)

oil.snv <- cbind(oil.data[,1:3], df)
```


## To have a pls-da plot

```{r plsda2, message=FALSE, warning=FALSE}

library(mixOmics)
## Data set

oil_data <- oil.snv[,4:573]
X <- oil_data

Country <- oil.snv[,3]
Y <- as.factor(Country)

summary(Y)

MyResult.splsda <- mixOmics::splsda(X,Y, keepX = c(10,15))

plotIndiv(MyResult.splsda, ind.names = FALSE, legend=TRUE,
          ellipse = TRUE, star = TRUE, title = 'sPLS-DA on geographical origin of oil',
          X.label = 'PLS-DA 1 (44%)', Y.label = 'PLS-DA 2 (20%)')

auc.plsda <- auroc(MyResult.splsda)

```

## Variable selection outputs

The contribution of selected variables for PLS-DA model:

```{r pls3, message=FALSE, warning=FALSE}
MyResult.splsda2 <- mixOmics::splsda(X,Y, ncomp=3, keepX=c(15,10,5))

plotLoadings(MyResult.splsda2, contrib = 'max', method = 'mean')

```

## Tuning parameters and numerical outputs

```{r pls4, message=FALSE, warning=FALSE}
MyResult.plsda2 <- mixOmics::splsda(X,Y, ncomp=10)
set.seed(30) # for reproducbility in this vignette, otherwise increase nrepeat
MyPerf.plsda <- perf(MyResult.plsda2, validation = "Mfold", folds = 3, 
                  progressBar = FALSE, nrepeat = 10) # we suggest nrepeat = 50

plot(MyPerf.plsda, col = color.mixo(5:7), sd = TRUE, legend.position = "horizontal")

list.keepX <- c(5:10,  seq(20, 100, 10))

list.keepX

set.seed(123)

tune.splsda.oil <- tune.splsda(X, Y, ncomp = 10,
                                 validation = 'Mfold',
                                 folds = 3, dist = 'max.dist', progressBar = FALSE,
                                 measure = "BER", test.keepX = list.keepX,
                                 nrepeat = 50)

error <- tune.splsda.oil$error.rate

ncomp <- tune.splsda.oil$choice.ncomp$ncomp

ncomp

select.keepX <- tune.splsda.oil$choice.keepX[1:ncomp]

select.keepX

```

## The final pls-da model using tuning setting

```{r pls5, message=FALSE, warning=FALSE}
MyResult.splsda.final <- mixOmics::splsda(X, Y, ncomp = ncomp, keepX = select.keepX)

plotIndiv(MyResult.splsda.final, ind.names = FALSE, legend=TRUE,
          ellipse = TRUE, star = TRUE, title = 'sPLS-DA on geographical origin of oil',
          X.label = 'PLS-DA 1 (30%)', Y.label = 'PLS-DA 2 (16%)')
```

## Discrimination accuracy based on traing and testing data

```{r PLSDA6, echo=TRUE, message=FALSE, warning=FALSE}
library(caret)
oildata <- cbind(Country, oil_data)

set.seed(100)

# Step 1: Get row numbers for the training data
trainRowNumbers <- createDataPartition(oildata$Country, p=0.7, list=FALSE)

# Step 2: Create the training  dataset
trainData <- oildata[trainRowNumbers,]

# Step 3: Create the test dataset
testData <- oildata[-trainRowNumbers,]

plsda_model <- caret::plsda(trainData[,2:571],factor(trainData$Country), ncomp = 6, probMethod = "Bayes")


C1 <- confusionMatrix(predict(plsda_model, trainData[,2:571]),as.factor(trainData$Country))

C2 <- confusionMatrix(predict(plsda_model, testData[,2:571]),as.factor(testData$Country))

```

The Confusion Matrix for geographical origin using training data
```{r plsda results_train}

C1

```

The Confusion Matrix for geographical origin using testing data
```{r plsda results_test}

C2

```

The overall accuracy for training set is **96%** and for testing set is **91%**.

